Choosing a Population Genomics Approach

### 2021-11-05 RADseq.Rmd
Added poolseq content

```{r,message = FALSE,echo = FALSE}
  library("knitcitations")
  library("knitr")
  cite_options(citation_format = "pandoc", max.names = 3, style = "html", hyperlink = "to.doc")
  bib <- read.bibtex("bibtexlib.bib")
  opts_chunk$set(tidy = FALSE, message = FALSE, warning = FALSE,
                 fig.width = 10, fig.height = 6, cache = TRUE)
  # use this to set knitr options:
  # http://yihui.name/knitr/options #chunk_options
```
---
title: 'RADseq'
subtitle: '*NJ Gr&uuml;nwald, ZN Kamvar, and SE Everhart*'
---

>>>>

```{r,message = FALSE,echo = FALSE}
  library("knitcitations")
  library("knitr")
  cite_options(citation_format = "pandoc", max.names = 3, style = "html", hyperlink = "to.doc")
  bib <- read.bibtex("bibtexlib.bib")
  opts_chunk$set(tidy = FALSE, message = FALSE, warning = FALSE,
                 fig.width = 10, fig.height = 6, cache = TRUE)
  # use this to set knitr options:
  # http://yihui.name/knitr/options #chunk_options
```
---
title: 'RADseq'
subtitle: '*Katherine Silliman, Danielle Davenport*'
---

### 2021-11-05 choosing-population-genetics.Rmd
Added poolseq content

Deciding on a sequencing approach for a new project can be challenging, and depends primarily on the questions you are interested in, but also constraints set by funding, existing genomic resources, sample size, genome characteristics, and expertise in the research group. The main categories of population genomic sequencing approaches are:

@@

Below we list a number of great review articles and empirical comparison studies that can help when making the decision. This topic was also discussed during the MarineOmics seminars (link).

Empiracal comparisions:

@@

Presently, our site covers four approaches (WGS=whole genome (re)sequencing):

>>>>

# Population genomic sequencing approaches
Deciding on a sequencing approach for a new project can be challenging, and depends primarily on the questions you are interested in, but also constraints set by funding, existing genomic resources, sample size, genome characteristics, and expertise in the research group. The main categories of population genomic sequencing approaches are:

@@

@@

# Recommended readings  
Below we list a number of great review articles and empirical comparison studies that can help when making the decision. This topic was also discussed during the MarineOmics seminars (link).

Empirical comparisons:

# MarineOmics Guidelines
Presently, our site covers four approaches:

* [RADseq](RADseq.html)  
* [hcWGS](WGS_intro.html)
* [lcWGS, maintained by MarineOmics member Nicolas Lou](https://github.com/therkildsen-lab/genomic-data-analysis/blob/master/lcwgs_data_analysis.md)
* [Poolseq](poolseq.html)
